An inventory of human light exposure related behaviour

### 2023-11-09 manuscript_SciRep.Rmd
Affiliation conflict resloved-MASj

affiliation:
  - id            : "1"
    institution   : "Monash Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Malaysia"
  - id            : "2"
    institution   : "Psychiatric Hospital of the University of Basel (UPK), Centre for Chronobiology, Basel, Switzerland"

  - id            : "3"
    institution   : "North South University, Department of History and Philosophy, Bangladesh"

>>>>

affiliation:
  - id            : "1"
    institution   : "Monash Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Malaysia"

  - id            : "2"
    institution   : "North South University, Department of History and Philosophy, Bangladesh"

  - id            : "3"
    institution   : "Psychiatric Hospital of the University of Basel (UPK), Centre for Chronobiology, Basel, Switzerland"

### 2023-11-09 manuscript_SciRep.tex
Affiliation conflict resloved-MASj

\affiliation{\vspace{0.5cm}\textsuperscript{1} Monash Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Malaysia\\\textsuperscript{2} Psychiatric Hospital of the University of Basel (UPK), Centre for Chronobiology, Basel, Switzerland\\\textsuperscript{3} North South University, Department of History and Philosophy, Bangladesh\\\textsuperscript{4} University of Basel, Transfaculty Research Platform Molecular and Cognitive Neurosciences, Basel, Switzerland\\\textsuperscript{5} Eindhoven University of Technology, Department of the Built Environment, Building Lighting, Eindhoven, Netherlands\\\textsuperscript{6} Eindhoven University of Technology, Intelligent Lighting Institute, Eindhoven, Netherlands\\\textsuperscript{7} Eindhoven University of Technology, Department of Industrial Engineering and Innovation Sciences, Human-Technology Interaction, Eindhoven, Netherlands\\\textsuperscript{8} Monash University, Department of Electrical and Computer Systems Engineering, Selangor, Malaysia\\\textsuperscript{9} University of Colorado Boulder, Department of Integrative Physiology, Boulder, USA\\\textsuperscript{10} Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA\\\textsuperscript{11} Translational Sensory \& Circadian Neuroscience, Max Planck Institute for Biological Cybernetics, Tübingen, Germany\\\textsuperscript{12} TUM School of Medicine and Health, Technical University of Munich, Munich, Germany\\\textsuperscript{13} TUM Institute of Advanced Study (TUM-IAS), Technical University of Munich, Garching, Germany\\\textsuperscript{+} Joint first author\\\textsuperscript{*} Corresponding Author}

>>>>

\affiliation{\vspace{0.5cm}\textsuperscript{1} Monash Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Malaysia\\\textsuperscript{2} North South University, Department of History and Philosophy, Bangladesh\\\textsuperscript{3} Psychiatric Hospital of the University of Basel (UPK), Centre for Chronobiology, Basel, Switzerland\\\textsuperscript{4} University of Basel, Transfaculty Research Platform Molecular and Cognitive Neurosciences, Basel, Switzerland\\\textsuperscript{5} Eindhoven University of Technology, Department of the Built Environment, Building Lighting, Eindhoven, Netherlands\\\textsuperscript{6} Eindhoven University of Technology, Intelligent Lighting Institute, Eindhoven, Netherlands\\\textsuperscript{7} Eindhoven University of Technology, Department of Industrial Engineering and Innovation Sciences, Human-Technology Interaction, Eindhoven, Netherlands\\\textsuperscript{8} Monash University, Department of Electrical and Computer Systems Engineering, Selangor, Malaysia\\\textsuperscript{9} University of Colorado Boulder, Department of Integrative Physiology, Boulder, USA\\\textsuperscript{10} Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA\\\textsuperscript{11} Translational Sensory \& Circadian Neuroscience, Max Planck Institute for Biological Cybernetics, Tübingen, Germany\\\textsuperscript{12} TUM School of Medicine and Health, Technical University of Munich, Munich, Germany\\\textsuperscript{13} TUM Institute of Advanced Study (TUM-IAS), Technical University of Munich, Garching, Germany\\\textsuperscript{+} Joint first author\\\textsuperscript{*} Corresponding Author}
